The \emph{SafeStreets} system shall be providing four main functions to various users; in this section, the system boundaries and scope used to define the limitations and different responsibilities of the system to be. 

The first of the main functionalities is the enabling of users to report traffic violations. Regarding this, some phenomena are regarded as world phenomena not viewed by the system due to its limitations such as the fact that the system does not directly detect a violation. However, it can be accounted for by the system through a traffic report made by the users. Moreover, another functionality that has to do with the users is the publishing of collected data to be viewed by the users in a refined representation to help them consider the safety of various areas based on traffic violations. The data is also communicated to the authorities but with different levels of details.

The other two main functions have to do with the \emph{SafeStreets} system providing services to government authorities. The domain limitations of the system affecting this interaction are also discussed in this section. Such as, the fact that the system is only able to make suggestions for preventive measures to the authorities based on the accident data that have been communicated. Meaning, that the system does not have any knowledge of accidents unless they are reported by the authorities and that the system can only suggest interventions and neither put them into place nor can detect them being applied. Moreover, a second function to the authorities would be the communication of traffic reports received from users to be later used by government officials to give out traffic tickets, the system responsibilities to support this process is to prevent the users from tampering with images \emph{digitally} and to provide the collected reports to the authorities proactively. In other words, physical tampering with license plates to mislead authorities and the actual process of giving out tickets is not part of the application domain. 

Below is a table summarizing and classifying the different phenomena that are related to the system functionalities. 
Main system functionalities:

\begin{itemize}
\item[$\rightarrow$] \emph{\textbf{F1:}} Reporting of violations
\item[$\rightarrow$] \emph{\textbf{F2:}} Communication of collected data to users
\item[$\rightarrow$] \emph{\textbf{F3:}} Suggestion of interventions
\item[$\rightarrow$] \emph{\textbf{F4:}} Communication of reports for ticketing
\end{itemize}
\input{table-World_and_Machine}
